\bf Are you normal? A new projection pursuit index to assess a sample against a multivariate null distribution

### 2024-07-03 paper.qmd
mapping out conclusions

To define a measure of an interesting projection is to maximize the **average Malahanobis distance in the projection** for a subset of points, $W$. The set of points could be chosen in different ways, but the default is those that are outside the specified ellipsoid in \pD{}. Alternatives could be to select a set of observations with the largest Mahalanobis distance, manually select observations or possibly a group of points identified via clustering of the extremes.

@@

This is implemented in the `tourr` (REF) package, where the projected ellipsoid can be drawn for each projection. The guided tour will take arguments specifying the data, and the null variance-covariance matrix.

@@

Say something about the relationship with @directional-outlyingness and Stahel-Donoho outlyingness

>>>>

To define a measure of an interesting projection is to maximize the average Mahahlanobis distance [@mahalanobis] in the projection for a subset of points, $W$. The set of points could be chosen in different ways, but the default is those that are outside the specified ellipsoid in \pD{}. Alternatives could be to select a set of observations with the largest Mahalanobis distance, manually select observations or possibly a group of points identified via clustering of the extremes.

@@

This is implemented in the `tourr` [@tourr;@tourr-cran] package, where the projected ellipsoid can be drawn for each projection. The guided tour will take arguments specifying the data, and the null variance-covariance matrix.

@@

Say something about the relationship with @directional-outlyingness and Stahel-Donoho outlyingness. This method could be implemented in the way we used to show ellipses, generate points on the surface of the irregular shape, overlay the data on this and make projections.

Difference from general outlier detection, see use of Mahalanobis distance in @filzmoser2018.

Potential new directions.

### 2024-07-03 paper.tex
mapping out conclusions

To define a measure of an interesting projection is to maximize the
\textbf{average Malahanobis distance in the projection} for a subset of
points, \(W\). The set of points could be chosen in different ways, but
the default is those that are outside the specified ellipsoid in \pD{}.
Alternatives could be to select a set of observations with the largest
Mahalanobis distance, manually select observations or possibly a group
of points identified via clustering of the extremes.

@@

This is implemented in the \texttt{tourr} (REF) package, where the
projected ellipsoid can be drawn for each projection. The guided tour
will take arguments specifying the data, and the null
variance-covariance matrix.

@@

Say something about the relationship with
\citet{directional-outlyingness} and Stahel-Donoho outlyingness

>>>>

To define a measure of an interesting projection is to maximize the
average Mahahlanobis distance \citep{mahalanobis} in the projection for
a subset of points, \(W\). The set of points could be chosen in
different ways, but the default is those that are outside the specified
ellipsoid in \pD{}. Alternatives could be to select a set of
observations with the largest Mahalanobis distance, manually select
observations or possibly a group of points identified via clustering of
the extremes.

@@

This is implemented in the \texttt{tourr} \citep{tourr, tourr-cran}
package, where the projected ellipsoid can be drawn for each projection.
The guided tour will take arguments specifying the data, and the null
variance-covariance matrix.

@@

Say something about the relationship with
\citet{directional-outlyingness} and Stahel-Donoho outlyingness. This
method could be implemented in the way we used to show ellipses,
generate points on the surface of the irregular shape, overlay the data
on this and make projections.

Difference from general outlier detection, see use of Mahalanobis
distance in \citet{filzmoser2018}.

Potential new directions.
